\documentclass[11pt]{article}

\include{setup}
\include{about}
\include{education}

\begin{document}

\title{R\'esum\'e}
\author{\FULLNAME}

\maketitle{\selectlanguage{spanish}\today}

\makeabout
    {Acerca de Mi}{Conocimientos Tecnicos}
    {
      I spend most of my professional career maintaining and designing high-scalable Linux systems.
      More recently, I have been learning how those systems are built from the programming side.
    }

\section{Job Experience}


\subsection{Email Hosting Software Engineer III --- Web.com \hfill 2017-2018}
\begin{itemize}
\item Continuing the OS migration now on the shared email platform. From using \texttt{qmail} to \texttt{postfix}.
\item Implemented a centralized logging solution based on the \texttt{Fluentd}, \texttt{Postgresql} and \texttt{Grafana}.
\item Automated \texttt{qemu} vm creation for non-production environments, using ansible.
\item Deployed a \texttt{kubernetes} cluster for running \texttt{selenium} integration tests.
\end{itemize}

\subsection{Web Hosting Software Engineer II --- Web.com \hfill 2014-2016}
\begin{itemize}
\item Development on a dynamic ssl web proxy, based on \texttt{nginx} and \texttt{lua}. Backed by \texttt{redis}.
\item Troubleshooting issues on a multi-network \texttt{Wordpress} installation. Backed by \texttt{mysql} Percona Cluster.
\item Single-handedly migrated part of the web hosting platform from Gentoo to RedHat using \texttt{Ansible}.
\end{itemize}

\subsection{Web Hosting Software Engineer I --- Web.com \hfill 2011-2013}
\begin{itemize}
\item Troubleshooting L3 customer support requests on a \texttt{LAMP} based shared hosting platform.
\item OS maintainer of a Gentoo Linux fork used across the shared hosting platform. From kernel to libraries.
\end{itemize}

\subsection{Jr. Linux System Administrator --- Sols S.A. \hfill 2011}
\begin{itemize}
\item Network design and deploy of a \texttt{OpenVPN} node and \texttt{Squid} proxy. Maintenance and technical support.
\end{itemize}


\makeeducation
    {Educacion}{Idiomas}
    {Ingles}{Intermedio}
    {Español}{Nativo}


\section{Proyectos Personales}

\hypersetup{urlcolor=gray}
\begin{center}
  \begin{tabular}{ c l }
    \project{Common Lisp} {scenic}         {varios motores graficos, y sequenciadores de MIDI}
    \project{Golang}      {cli-view}       {clientes de terminal, para ver los comentarios de diferentes sitios}
    \project{Elm}         {newspod}        {motor de busqueda online de podcasts}
    \project{C}           {sleeper}        {monitoreo y almacenamiento en sqlite de eventos X11}
    \project{Erlang}      {snitch}         {monitor of public dns records}
    \project{React}       {reddit-gallery} {galeria de imagenes para reddit}
    \project{Javascript}  {zoom2srt}       {webapp para convertir chats de Zoom exportados en .txt en subtitulos .srt}
  \end{tabular}
\end{center}

\end{document}
